An Aliasing-Tolerant Parallel Programming Model

### 2012-11-13 doc/types-pldi2013/evaluation.tex
Working on figures to make the prettier and easier to understand
mods

\subsection{Checking Overhead}
\label{subsec:overhead}
The first Legion implementation consisted of a C++ library of Legion primitives
\cite{Legion12} with no checking of region memory accesses.  
When testing applications on this system we frequently encountered memory corruption due to
illegal region accesses caused by application bugs.
In many cases, this corruption occurred between nodes in the cluster or on 
GPUs, environments for which debugging tools are primitive at best.
%  Finding these bugs required either multiple {\tt gdb} sessions 
%for observing execution on different nodes simultaneously or using {\tt printf} for debugging on
%GPUs.  
To locate the application bugs causing these illegal accesses, we initially added 
dynamic checks on  all region accesses for both CPUs and GPUs which  
added considerable runtime overhead.  
To preserve the benefit of checking every access without the cost of dynamic checks, we implemented the type, privilege, and coherence checker we have described. 
We then rewrote the applications in this language and type checked them, at which point the
dynamic region access checks could be safely elided.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{figs/circuit_96_popl.pdf}
\end{center}
\vspace{-2mm}
\caption{Overhead for the Circuit simulation with 96 total pieces.\label{fig:ckt_overhead}}
\vspace{-6mm}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{figs/fluid_19200_popl.pdf}
\end{center}
\vspace{-2mm}
\caption{Overhead for the Fluid simulation with 19200 cells.\label{fig:fluid_overhead}}
\vspace{-6mm}
\end{figure}

@@

\begin{figure}
\begin{center}
\subfigure[4096 cells per dimension]
{
\includegraphics[scale=0.33]{figs/amr_4096_popl.pdf}
\label{fig:amr4096}
}
\subfigure[8192 cells per dimension]
{
\includegraphics[scale=0.33]{figs/amr_8192_popl.pdf}
\label{fig:amr8192}
}
\subfigure[16384 cells per dimension]
{
\includegraphics[scale=0.33]{figs/amr_16384_popl.pdf}
\label{fig:amr16384}
}
\end{center}
\vspace{-2mm}
\caption{Overhead for the AMR application.\label{fig:amr_overhead}}
\vspace{-6mm}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{figs/circuit_coherence.pdf}
\end{center}
\vspace{-2mm}
\caption{Performance gains from relaxed coherence modes.\label{fig:circuit_excl}}
\vspace{-6mm}
\end{figure}

>>>>

\subsection{Checking Overhead}
\label{subsec:overhead}
The first Legion implementation consisted of a C++ library of Legion primitives
\cite{Legion12} with no checking of region memory accesses.  
When using this system we frequently encountered memory corruption due to
illegal region accesses caused by application bugs.
In many cases, this corruption occurred between nodes in the cluster or on 
GPUs, environments for which debugging tools are primitive at best.
%  Finding these bugs required either multiple {\tt gdb} sessions 
%for observing execution on different nodes simultaneously or using {\tt printf} for debugging on
%GPUs.  
To locate the application bugs causing these illegal accesses, we initially added 
dynamic checks on  all region accesses for both CPUs and GPUs which  
added considerable runtime overhead.  
To preserve the benefit of checking every access without the cost of dynamic checks, we implemented the type, privilege, and coherence checker we have described. 
We then rewrote the applications in this language and type checked them, at which point the
dynamic region access checks could be safely elided.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.30]{figs/circuit_96_popl.pdf}
\end{center}
\vspace{-2mm}
\caption{Overhead for the Circuit simulation with 96 total pieces.\label{fig:ckt_overhead}}
\vspace{-5mm}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.30]{figs/fluid_19200_popl.pdf}
\end{center}
\vspace{-2mm}
\caption{Overhead for the Fluid simulation with 19200 cells.\label{fig:fluid_overhead}}
\vspace{-5mm}
\end{figure}

@@

\begin{figure}
\begin{center}
\subfigure[4096 cells per dimension]
{
\includegraphics[scale=0.30]{figs/amr_4096_popl.pdf}
\label{fig:amr4096}
}
\subfigure[8192 cells per dimension]
{
\includegraphics[scale=0.30]{figs/amr_8192_popl.pdf}
\label{fig:amr8192}
}
\subfigure[16384 cells per dimension]
{
\includegraphics[scale=0.30]{figs/amr_16384_popl.pdf}
\label{fig:amr16384}
}
\end{center}
\vspace{-2mm}
\caption{Overhead for the AMR application.\label{fig:amr_overhead}}
\vspace{-8mm}
\end{figure}

@@

\begin{figure}
\begin{center}
\subfigure[48 Piece Problem Size]
{
\includegraphics[scale=0.18]{figs/circuit_coherence_48.pdf}
\label{fig:circuit_excl_48}
}
\subfigure[96 Piece Problem Size]
{
\includegraphics[scale=0.18]{figs/circuit_coherence_96.pdf}
\label{fig:circuit_excl_96}
}
\end{center}
\vspace{-4mm}
\caption{Performance of relaxed coherence modes.\label{fig:circuit_excl}}
\vspace{-6mm}
\end{figure}
%\begin{figure}
%\begin{center}
%\includegraphics[scale=0.33]{figs/circuit_coherence.pdf}
%\end{center}
%\vspace{-2mm}
%\caption{Performance gains from relaxed coherence modes.\label{fig:circuit_excl}}
%\vspace{-6mm}
%\end{figure}
